HO unification from object language to meta language

### 2024-02-15 main.tex
update tex

\def\ol{\acronym{ol}} % object language
\def\ml{\acronym{ml}} % meta language
\def\lf{\acronym{lf}} % logical framework

@@

\begin{tcolorboxSimple}
  \begin{tabular}{c|c}
    \begin{minipage}[c]{0.50\linewidth}
      \begin{elpicode}
        kind term type.
        type const gref -> term.
        type app list term -> term.
        type fun (term -> term) -> term.
        type prod (term -> term) -> term.
      \end{elpicode}
    \end{minipage}
    &
    \begin{minipage}[c]{0.46\linewidth}
      \begin{textcode}
        Example:
        a        ==> const 0
        f a      ==> app[const f, const a]
        ~$\lambda$~x => x  ==> fun x\ x
        ~$\forall$x, F x~  ==> prod x\ app[F, x]
      \end{textcode}
    \end{minipage}
  \end{tabular}
\end{tcolorboxSimple}

@@

The \coq instance on the left is compiled in the \elpi rule on the right. If 
we try to solve the following query (already in the \elpi syntax)

\elpiIn{tc-Decision (prod x\ app[f, y, x])}

where \coqIn{f : A -> B -> Type} and \coqIn{y: A}, we can notice that the \elpi
rule above cannot be applied; the terms \elpiIn{prod x\ app[P, x]} and
\elpiIn{prod x\ app[f, y, x]} cannot unify since the lists under the
\elpiIn{app} constructors are of different length.\todo{NOTE: the goal unify
with forall\_dec in coq xké fa unif FO approx}

An other example of unification failure in the

\begin{itemize}
  \item TODO: context
  \item TODO: example
  \item TODO: riassunto delle next sections
\end{itemize}

>>>>

\def\ol{\acronym{ol}} % object language
\def\ml{\acronym{ml}} % meta language
\def\lf{\acronym{lf}} % logical framework
\def\ho{\acronym{ho}} % higher order

@@

\begin{tcolorboxSimple}
  \begin{tabular}{c|c}
    \begin{minipage}[c]{0.50\linewidth}
      \begin{elpicode}
        kind term type.
        type const gref -> term.
        type app list term -> term.
        type fun (term -> term) -> term.
        type prod (term -> term) -> term.
      \end{elpicode}
    \end{minipage}
    &
    \begin{minipage}[c]{0.48\linewidth}
      \begin{textcode}
        Example:
        a       ==> const 0
        f a     ==> app[const `f, const `a]
        ~$\lambda$~x => x ==> fun x\ x
        ~$\forall$x, F x~ ==> prod x\ app[F, x]
      \end{textcode}
    \end{minipage}
  \end{tabular}
\end{tcolorboxSimple}

@@

The \coq instance on the left is compiled in the \elpi rule on the right. If the 
query to solve (already in the \elpi syntax) is

\elpiInEq{tc-Decision (prod x\ const `nat)}

\noindent it is clear that the \elpi rule above will not unify with the query,
Since the rigid node \elpiIn{app} is different from the rigid node
\elpiIn{const}. The problem come form the lost of the fact that \coqIn{P} is an
higher-order variable in \coq, and in \elpi it is translated into a first order
variable (the variable \elpiIn{P} in \elpi does not see the binder \elpiIn{x}).

Another unification problem we can da notare che il problema dopo, is the FO
approx. Coq applica la regola forall\_dec sul goal (prod x\ app[f, y, x]), ma forse 
bisognerebbe vedere se altri solver accettano questa euristica. Così facciamo 
vedere che non siamo i soli a farlo. Nel caso contrario bisogna dire come funziona
l'algo di unif di coq in questo caso specifico

\elpiInEq{tc-Decision (prod x\ app[const `f, const `y, x])}

Specificare anche che non riusciamo a fare ne eta ne beta riduzione.

Dire che elpi unifica in HO e con eta-beta

% where \coqIn{f : A -> B -> Type} and \coqIn{y: A}, we can notice that the \elpi
% rule above cannot be applied; the terms \elpiIn{prod x\ app[P, x]} and
% \elpiIn{prod x\ app[f, y, x]} cannot unify since the lists under the
% \elpiIn{app} constructors are of different length.\todo{NOTE: the goal unify
% with forall\_dec in coq xké fa unif FO approx}

% Another example of unification failure is given by the the following instance
